---
title: "Main code of analysis of mtcars data"
author: "Farzana Amin"
date: "Oct 1, 2020"
output:
  ioslides_presentation: default
  html_document:
    number_sections: yes
    toc: yes
  slidy_presentation: default
mode: selfcontained
job: Reproducible Pitch Presentation
subtitle: Variables and MPG
highlighter: highlight.js
widgets: bootstrap
keep_md: true
---

## Coursera Reproducible Pitch

### See the Regression Models Course Project  

- URL: *https://github.com/Farzana1234/DDP_week4_project*
- The details of the whole project and files are at this URL including the shinyapp.

---

## mtcars Dataset

### Motor Trend Car Road Tests

> The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models).
### Source
> Henderson and Velleman (1981), Building multiple regression models interactively. Biometrics, 37, 391-411.
```{r}
library(datasets)
head(mtcars, 3)
```
---

## mtcars Dataset - Format

**A data frame with 32 observations on 11 variables.**

| Index | Field | Detail |
------- | ----- | ------ |
| [, 1] | mpg | Miles/(US) gallon |
| [, 2]  | cyl | Number of cylinders |
| [, 3]	| disp | Displacement (cu.in.) |
| [, 4]	| hp | Gross horsepower |
| [, 5]	| drat | Rear axle ratio |
| [, 6]	| wt | Weight (lb/1000) |
| [, 7]	| qsec | 1/4 mile time |
| [, 8]	| vs | V/S |
| [, 9]	| am | Transmission (0 = automatic, 1 = manual) |
| [,10]	| gear | Number of forward gears |
| [,11]	| carb | Number of carburetors |

---

## Analysis - Main Code incluing ui.R and server.R. 
#### The ui.R code is quite long so only putting server.R code here

```{r}
library(shiny)
library(datasets)

mpgData <- mtcars
mpgData$am <- factor(mpgData$am, labels = c("Automatic", "Manual"))

shinyServer(function(input, output) {
  
  formulaText <- reactive({
    paste("mpg ~", input$variable)
  })
  
  formulaTextPoint <- reactive({
    paste("mpg ~", "as.integer(", input$variable, ")")
  })
  
  fit <- reactive({
    lm(as.formula(formulaTextPoint()), data=mpgData)
  })
  
  output$caption <- renderText({
    formulaText()
  })
  
  output$mpgBoxPlot <- renderPlot({
    boxplot(as.formula(formulaText()), 
            data = mpgData,
            outline = input$outliers)
  })
  
  output$fit <- renderPrint({
    summary(fit())
  })
  
  output$mpgPlot <- renderPlot({
    with(mpgData, {
      plot(as.formula(formulaTextPoint()))
      abline(fit(), col=2)
    })
  })
  
})

```

